\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-01-20 paper/subdocuments/data_and_methods.Rnw
data update, gini-series (graphic) draft

\subsubsection{Descriptives - where do we put this?}
nice grapics for taxable income, reines einkommen and income after taxes here...

>>>>

\subsubsection{Descriptives - where do we put this?}
nice grapics for taxable income, reines einkommen and income after taxes here...
<<different_ginis>>=
df$G_reink[df$G_reink==1]<-NA
df$G_taxed[df$G_taxed==1]<-NA
ggplot(df[df$kanton=="CH",], aes(x=steuerperiode,y=G_steink))+geom_line()+facet_wrap(~kanton)+geom_line(aes(y=G_reink),color="blue")+geom_line(aes(y=G_taxed),color="green")
ggplot(df, aes(x=steuerperiode,y=G_steink))+geom_line()+facet_wrap(~kanton)+geom_line(aes(y=G_reink),color="blue")+geom_line(aes(y=G_taxed),color="green")
@
